Sodium silicate and hexametaphosphate promote the release of (oxyhydr)oxide nanoparticles from corroding iron

### 2022-06-17 Rmarkdown/paper-si.Rmd
added session info

>>>>

```{r table-s1}
tibble::tribble(
  ~Parameter, ~Value,
  "Injection volume", "50 µL",
  "Spacer", "500 µm",
  "Total run time", "33.5 min",
  "Detector flow", "1 mL min^-1^",
  "Injection flow", "0.2 mL min^-1^",
  "Focus flow", "1.5 mL min^-1^",
  "Focus period", "5 min",
  "Transition period", "1 min",
  "Crossflow", "2 mL min^-1^ ",
) %>% 
  knitr::kable(caption = "**Table S1.** FFF run parameters for globular protein standards.")
```

### 2022-06-17 Rmarkdown/paper.Rmd
remove .DS_Store
added session info

```{r table-run-params, echo=FALSE}
tibble::tribble(
  ~Parameter, ~Value,
  "Injection volume", "0.25 (sodium silicate) and 0.5 mL (hexametaphosphate)",
  "Spacer", "500 µm",
  "Total run time", "53 min",
  "Detector flow", "1 mL min^-1^",
  "Injection flow", "0.2 mL min^-1^",
  "Focus flow", "2.8 mL min^-1^",
  "Focus period", "10 min",
  "Transition period", "1 min",
  "Initial crossflow", "2 mL min^-1^ (first 31 min of each run)",
  "Crossflow decay", "Linear over 2 min",
  "Final crossflow", "0.1 mL min^-1^ (10 min)",
  "Rinse step", "10 min (no crossflow)"
) %>% 
  knitr::kable(caption = "FFF run parameters.")
```

@@

The deviation of the channel thickness from its nominal value of 500 µm was estimated using a method described elsewhere [@litzen_separation_1993], using ferritin and bovine serum albumin as globular protein standards with diffusion coefficients taken from literature [@clough_role_1981; @gaigalas_diffusion_1992].

@@

>>>>

```{r table-run-params}
tibble::tribble(
  ~Parameter, ~Value,
  "Injection volume", "0.25 (sodium silicate) and 0.5 mL (hexametaphosphate)",
  "Spacer", "500 µm",
  "Total run time", "53 min",
  "Detector flow", "1 mL min^-1^",
  "Injection flow", "0.2 mL min^-1^",
  "Focus flow", "2.8 mL min^-1^",
  "Focus period", "10 min",
  "Transition period", "1 min",
  "Initial crossflow", "2 mL min^-1^ (first 31 min of each run)",
  "Crossflow decay", "Linear over 2 min",
  "Final crossflow", "0.1 mL min^-1^ (10 min)",
  "Rinse step", "10 min (no crossflow)"
) %>% 
  knitr::kable(caption = "FFF run parameters.")
```

@@

The deviation of the channel thickness from its nominal value of 500 µm was estimated using a method described elsewhere [@litzen_separation_1993], using ferritin and bovine serum albumin as globular protein standards with diffusion coefficients taken from literature [@clough_role_1981; @gaigalas_diffusion_1992]. The FFF method for the globular protein runs is summarized in Table S1.

@@

```{r session-info}
writeLines(capture.output(devtools::session_info()), "session-info.txt")
```
